---
title: "scratch"
author: "Joe Cheng <joe@rstudio.com>"
date: "June 27, 2014"
output: html_document
---



# Reactivity in Shiny

The `input` object presents user input as *reactive values*.
```{r eval=FALSE}
input$n # read
```

The `reactive()` function is used to define *reactive expressions*: calculated values based on user input.
```{r eval=FALSE}
randomData <- reactive( runif(input$n) ) # define
randomData() # read
```
`renderText`, `renderPlot`, and other `render`-prefix methods are used to create outputs.
```{r eval=FALSE}
output$baz <- renderPlot( hist(randomData()) )
```


## Foo

It depends on who you ask.

Changing inputs can trigger *recalculations* and *side effects*.

The traditional solution for interactivity is callback oriented programming.


updatePlot <- function() {
  selectedData <- iris[,c(input$x, input$y)]
  clusters <- kmeans(selectedData, input$clusters)
  par(mar = c(5.1, 4.1, 0, 1))
  plot(selectedData,
       col = clusters$cluster,
       pch = 20, cex = 3)
  points(clusters$centers, pch = 4, cex = 4, lwd = 4)
}

input$onChange("x", function(value) {
  updatePlot()
})

input$onChange("y", function(value) {
  updatePlot()
})

input$onChange("clusters", function(value) {
  updatePlot()
})


selectedData <- reactive({
  iris[,c(input$x, input$y)]
})
clusters <- reactive({
  kmeans(selectedData(), input$clusters)
})
output$plot <- renderPlot({
  par(mar = c(5.1, 4.1, 0, 1))
  plot(selectedData,
       col = clusters$cluster,
       pch = 20, cex = 3)
  points(clusters$centers, pch = 4, cex = 4, lwd = 4)
})





```{r echo=FALSE,results='hold'}
flowLayout(
  numericInput('degrees', 'Angle (degrees)', 90),
  numericInput('radius', 'Radius', 3)
)
```
```{r}
radians <- reactive( input$degrees * pi / 180 )
```

Angle (radians): `r renderText(radians())`

```{r}
arcLength <- reactive( radians() * input$radius )
```
Arc length: `r renderText(arcLength())`
